Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-05-19 paper/Analisis.tex
Escape fraction text

Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others. In order to study this in more detal FIG.(CLARA plot)

@@

>>>>

As a final test we compare our results with the analytical solution of the slab developed by (Neufeld 1990) Fig. ~\ref{figure:efvsNeufeld}, as the geometry we use is different from the one described for Neufeld, we dont expect the same results, in fact we found that for the homogenous sphere the escape fraction is higer than the slab (see ref, mark). Also we notest that for $\tau<10^{6}$ the escape fraction does not increase as it will be expected, This is due to the fact that the condition $a\tau_{h}>>\tau_{d}$ in not valid anymore.

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{Neufeld.png}
 \label{figure:efvsNeufeld}\caption{Escape fraction of this work compared with Neufeld analytical solution} 
\end{figure}
